---
title: "Forest Fire"
author: "Alvaro Guijarro"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Forrest Fire Visualization Practice

Lets download the Forest Fire information and see the names of the columns. 
```{r forrest fires}
forest_fire <- read.csv("forestfires.csv")
colnames(forest_fire)
```
The columns included in this dataset have the following meaning: 

* **X**: X-axis spatial coordinate within the Montesinho park map: 1 to 9 
* **Y**: Y-axis spatial coordinate within the Montesinho park map: 2 to 9 
* **month**: Month of the year: 'jan' to 'dec' 
* **day**: Day of the week: 'mon' to 'sun' 
* **FFMC**: Fine Fuel Moisture Code index from the FWI system: 18.7 to 96.20 
* **DMC**: Duff Moisture Code index from the FWI system: 1.1 to 291.3 
* **DC**: Drought Code index from the FWI system: 7.9 to 860.6 
* **ISI**: Initial Spread Index from the FWI system: 0.0 to 56.10 
* **temp**: Temperature in Celsius degrees: 2.2 to 33.30 
* **RH**: Relative humidity in percentage: 15.0 to 100 
* **wind**: Wind speed in km/h: 0.40 to 9.40 
* **rain**: Outside rain in mm/m2 : 0.0 to 6.4 
* **area**: The burned area of the forest (in ha): 0.00 to 1090.84 

Let's now see what are the first values contained in the "forestfire" dataset. 
```{r}
head(forest_fire,5)
```

### Data Processing

Let's see the columns of "month" and "day". 

```{r}
forest_fire %>% pull(month) %>% unique
forest_fire %>% pull(day) %>% unique
```
We can see that these values have the names of the months and days, and R would simply sort them by alphabetical order. Because of this, we have to give them the right order.

```{r}
month_order <- c("jan", "feb", "mar","apr", "may", "jun",
                 "jul", "aug", "sep","oct", "nov", "dec")
week_order <- c("mon", "tue", "wed", "thu", "fri", "sat","sun")
forest_fire <- forest_fire %>% 
  mutate(
    month = factor(month, levels = month_order),
    day = factor(day, levels = week_order)
  )

```
### When Do Most Forest Fires Occur?

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

